LaTeX draft for \\"Ancient Greece Yuri Visual Novel"

### 2015-10-04 text/draft.tex
Complete (very roughly) the garden path

\chapter{Where it all starts}

@@

\begin{comment}
Most must be already quite drunk, especially the athletes who already enjoyed a \emph{generous} meal after their morning achievements.\\

I feel fire rising to my cheeks.

As per tradition, the morning was filled with numerous sportive events. Nothing as glorious as the Olympic games, but still a good deal of different competitions: jumping, wrestling, javelin throws, horse races... But I have little memories of all of them, completely eclipsed by the one which dried out my throat. The foot race.\\

More exactly, it's not the competition itself which left me unable to speak. I cannot even remember the name of the one who won it. But I do remember that she took part in it.

It's not that unusual for a woman to participate in such an event. Actually, there is often a token Spartan female athlete alongside the males, and they generally do quite well.

But that was not any woman. That was her.\\

These events are before everything else a present to the gods, and the competitors must be as resplendent as they are skilled, the sight of their nude bodies as much an offering as their actual performances.\\

And resplendent she was.\\

I helped her oiled herself before dawn, but there is a total difference between watching a greasy skin from close under the weak light of a candle and contemplating it shining under the bright sun.

A thousand reflections were stressing each line, each curve of her body, every movement of her sculpted muscles revealing a new feature, a new detail, a new wonder, in a never-ceasing display of beauty.
She had gathered her hair in a strict bun, but that only managed to stress out her face, her eyes, nose, lips, making them cuter than ever.\\

\dcomment{
	Description willingly vague while awaiting for illustrations.
	Of course, it's/it will be Ambrosia magnified vision, not necessarily the whole truth.
}

Enthralled, I was unable to look at anything else for the entire duration of the race, from the moment she entered the field to the last second before she retreated in the temple, out of sight.

Her expression when she covered the final meters, her reddish face transfigured from the intense action, her determined eyes looking far beyond the final line, is engraved in my memory. From that image alone, I can almost feel the shortness of her warmth breath, the drops of sweat running along her forehead, her brows, her cheeks, her lips...\\

I break the daydreaming at that point, remembering where I am, trying to appear attentive to the music.

But a little more self-control only saves face. It does not solve the real problem, in the same way this morning show did not start the fire in my heart.

It only poked a blaze which has been existing for months.\\

And, in spite of my mild efforts, my thoughts go wild once again.\\

I met her for the first time about four months ago. The group of wandering musicians I was with before had decided to remain in the Pieria region, renowned for its artists, but I was not so eager with the idea of setting up so young, and decided to continue my travels without them.\\

However, the roads of the peninsula are far from safe. The law pretty much ceases to exist as soon as the walls of the city are behind you and the wilderness is home to many four-legged and two-legged beasts.\\

Traveling alone never was an option, especially for someone like me, never trained in fighting and survival.

So I searched for a companion. And I found one quite easily.\\

She proposed herself as a mercenary, a bodyguard, even a porter, any job actually, as long as it would allow her to leave the area immediately.

She was clearly fleeing something, but she refused to talk about that. The only real information I got about her at that time was her name.\\

\foreignlanguage{greek}{Ἀντιόπη}. Antiope.\\

The safe option would have been to disregard such a shady offer. But she was a trained warrior, from one of those bellicose states where women are still taught the art of war alongside the men, and filled all my criteria for the ideal travel companion. She had both the skills I searched for and the will to roam the land. For free.\\

Maybe cold logic was not the only reason I accepted. Maybe, even back then, she was already bypassing my conscious mind to reach for a deeper and powerful part of myself. I cannot really say, and it's of little importance.\\

We departed together the next day. After a few hours of walking, I was in the middle of nowhere with an armed stranger who could have killed and looted me with the utmost ease.\\

She did not. She was as trustworthy that I thought – felt – she was.\\

After that, we traveled, ate, lived together for weeks and weeks, from city to city.

While in town, I was earning money with my songs and lyre. While in the wild, she was taking care of finding food and shelter.

A profitable association for both of us.\\

Yet it has slowly become unbearable for me. Not because I have grown to hate her manners and habits after watching them from close for months. The exact opposite actually.\\

At this very moment, I am completely enamored, infatuated, entranced, fascinated, captivated, ensorcelled, obsessed with her.\\

As soon as my thoughts are free from any immediate preoccupation, they fly right back at her. To be separated from her, even for a few hours, breaks my heart. Even in my sleep, I literally dream about her.\\

\end{comment}

\chapter{A talk}

@@

\begin{itemize}
	\item \glink{It's nothing}{Reassure her}
	\item \glink{The garden}{Ask if we can discuss somewhere else}
\end{itemize}

@@

I should probably scold her for her rude behavior. But I cannot resolve myself to do it. Partly because I realize I really want to go out. Partly because I'm somehow happy, even if this happiness is tainted with guilt, that she is worried about me, that did not hesitate for one second to discard all decorum for me.

TODO: Continue

@@

>>>>

\chapter*{Where it all starts}

@@

\chapter*{A talk}

@@

\begin{itemize}
	\item \glink{It's nothing}{Reassure her}
	\item \glink{The garden}{Ask if we can discuss it somewhere else}
\end{itemize}

@@

I should probably scold her for her rude behavior. But I cannot resolve myself to do it. Partly because I realize I really want to go out. Partly because I'm somehow happy, even if this happiness is tainted with guilt, that she is worried about me, that did not hesitate for one second to discard all decorum for me.\\

\dcomment{
	Reuse the garden description, because I'm that lazy
}

Now what we're outside, that the cold of the night contrast with the fire of our bodies, we take a break then a walk, strolling lazily through the gardens.\\

\speaker{Antiope} "Feeling better?"\\

I turn my head, my heart pounding, at the first actual words, and not grunts, coming out of Antiope's mouth since she took charge. And I nod to them like an afraid mouse.\\

\speaker{Antiope} "So, what's all that about?"\\

I rise my hand to ask for a pause. The  building is touching the close forest, and we certainly did get over the invisible frontier between the gardens and the woods. The trees are taller, the sky less visible, only a few stars and the moon peeking through the branches. We bath in the false silence of nature, these many little noises of an intense vegetable and animal life void of humans. Only the two of us alone in the world.\\

\begin{itemize}
	\item \glink{Blunt}{Straight to the point}
	\item \glink{Backstory}{A subtle approach}
\end{itemize}

@@

\gsection{Blunt}

I feel like if I don't say it \emph{now}, I will never say it. That if I don't tell things clearly and loudly, they're going to be misinterpreted.\\

So I turn myself to face Antiope. I breath hardly, too quickly, hyperventilating like mad. I force my elocution to form proper, articulate words, using all my professional tricks to sound as clear as humanly possible.\\

\speaker{Ambrosia} "I. Love. You."\\

As soon as the last syllable dies, I start panicking again. My whole body is paralyzed with fear, I'm unable to move, to look away, to speak. But under the skin, every little part of my organism is racing furiously.\\

Antiope is bewildered. Clueless. My sudden outburst takes several seconds to reach her brain, and a lot more to be processed. She blinks a few times, then repeats :\\

\speaker{Antiope} "You... Love... Me?"\\

I nod, a large smile engraved on my face. Antiope appears embarrassed, her right hand fidgeting on her left hip. She struggles to find her words, her tone pitching irregularly.\\

\speaker{Antiope} "That's an \emph{unexpected} declaration. Were you \emph{stressed} because you were \emph{planning} it?"\\

I nod again, even if I refrain a frown at the way she presents it. Like if the whole day had gone according to my design to trap her in this distant place. And she acts like a solider suspecting an ambush. Actually, her tic is similar to playing with the pommel of an invisible sword.\\

\speaker{Antiope} "I'm sorry but I have no \emph{romantic} interest in you Ambrosia."\\

She is really defensive, talking  like... Like how she used to talk when we first met. Keeping her distance, speaking little. She did defrost with time, but she suddenly is as icy as before.\\

\speaker{Antiope} "Is that all you wanted to tell me?"\\

I nod again, unable to do anything else.\\

\speaker{Antiope} "Fine. I think we should go back then. It's cold there."\\

I agree silently and follow her as she traces her way back to the building without looking behind even once.\\

\gsection{Backstory}

I don't know how to approach the subject. I have devised a thousand ways to do so, but none seems right. Antiope can have extreme instinctive reactions, and I don't want any bad word to trigger one. I decide to start by the beginning.\\

\speaker{Ambrosia} "Do you remember our first days together? We were going to Delphi by the land road, a trip of a few weeks through scarcely populated regions."\\

Antiope cocks an eyebrow but answers.\\

\speaker{Antiope} "Of course I remember. A damn eventful trip. We even nearly got attacked by bandits once. If we hadn't spot their lookout and made a detour, things would have turned ugly."\\

She displays a crooked smile at the evocation of missed violence.\\

\speaker{Ambrosia} "Do you remember what we discussed during these long days and nights?"\\

Antiope thinks for a few seconds, gathering her memories.\\

\speaker{Antiope} "Actually... I don't. Is there something I've forgotten? Something you told me... or that I told you?"\\

She suddenly raises up her defences. The idea of having let go any dangerous piece of information about herself in an instant of weakness triggered her alarm signal hard. I reassure her, even if slightly unnerved.\\

\speaker{Ambrosia} "Far from it. Actually, it's normal you don't remember... Because there is nothing worth remembering. We pretty much didn't talk to each other back then. Sure, we did exchange civilities and factual data about our environment and planning... But that's all. No actual conversation."\\

\speaker{Antiope} "Ah, yes... I wasn't really talkative back then."\\

\speaker{Ambriosa} "\emph{Withdrawn} would be a more exact term. But slowly, you began to speak more openly. Can you explain why?"\\

\speaker{Antiope} "I never really thought about this. I guess it's happened naturally. At first, we were pretty much strangers traveling together, and I was more wary than friendly. I'm not the kind to fake amicability in such situations. It's only with time passing that things got better."\\

\speaker{Ambriosa} "How?"\\

\speaker{Antiope} "How?"\\

She seems completely lost.\\

\speaker{Ambrosia} "How did they get better?"\\

\speaker{Antiope} "I guess... I leaned to trust you, began to relax more when being with you and... Damn, Ambrosia, you're far better are putting this feelings' stuff into words than me. Why the questioning?"\\

\speaker{Ambrosia} "Antiope, believe me, it's important."\\

\speaker{Antiope} "You're trying to make me say something, even I can tell. But what? That we used to be strangers under the same roof before we actually turn to friends? That's not an abnormal evolution in a relationship, even if my character did not ease the process."\\

I nod, encouraging.\\

\speaker{Ambrosia} "You have all the keywords, the concepts. Not only people change with the passing of time, but their relationships also evolve. Ties which were inumaginable yesterday can grow freely today."\\

\speaker{Antiope} "Is this about your mentor?"\\

The question stuns me, but Antiope's mind is going downhill that way at full speed.\\

\speaker{Antiope} "I remember you evoking her a few times... And by the way you spoke about her, I got the idea you had a really close relationship. And now, we are at a festival where many musicians have gathered. You meet again did you?"\\

I have turned red as a tomato. I didnt' remember telling Antiope about Terpsichore... And especially not that much!\\

And now, she is looking at me with an unbearable knowing smile.\\

\speaker{Antiope} "Sorry, but I'm of no help for sentimental problems. But I'm sure you'll manage. Romance is your very life after all. Just be honest with her and everything will be alright."\\

No, no, no! You're completely misinterpreting!\\

Yet, I can't help by being troubled at how close of the truth she is somehow. Not so long ago, I did meet again Terpsichore by pure luck at a symposium where we both performed.\\

It was strange, awkward, nostalgic, interesting, passionate, enlightening. I'm absolutely certain I didn't tell a word of what happened that night to Antiope, but that fateful encounter helped me bring to closure some remaining issues about my past, and was indeed a major cobblestone in the road leading to this moment.\\

Antiope is now gently pushing me to go back to the party. She thankfully refrains from adding any "helpful" comment, but with each step leading me out of this sanctuary of tranquility, I feel sicker.\\

\begin{itemize}
	\item \glink{Forfeit}{Let go}
	\item \glink{Not so fast}{Fight back}
\end{itemize}

\gsection{Forfeit}

The perfect atmosphere, the perfect moment... And nothing went as expected.\\

I feel empty. Tired. Discouraged. I let myself by drawn back to the building, to the noise and the light, to the people and oblivion.\\

\gsection{Not so fast}

I take a good breath and stop her.\\

\speaker{Ambrosia} "No. That's not about that old affair. I'm talking about the future."\\

Antiope halts, surprised.\\

\speaker{Ambrosia} "I will not say that you're totally wrong about my apprenticeship..."\\

\speaker{Antiope} "Come on Ambrosia, I'm not the most subtle person ever, but I'm neither deaf or stupid."\\

\speaker{Ambrosia} "But that does not concern \emph{her}. That concerns \emph{you}."\\

Silence. Antiope stares at me, her gaze inscrutable. No escape now.\\

\speaker{Ambrosia} "Antiope, I love you."\\

\dcomment{
	Not so different from \glink{Declaration}{this end}. To be merged, with some subtle differences (Antiope didn't reveal anything about herself on this path, the deal is unfair with Ambrosia now transparent)
}
